Future cosmic microwave background delensing with galaxy surveys

### 2017-12-04 Notes/referee_response.tex

\vspace{1cm}

\item
The author uses iterative internal delensing noise levels for the
CMB. I believe this could be discussed in more details. Can he specify
what multipole range is considered for this calculation ? I suppose
this multipole range should not overlap with the primordial B that is
used for constraints on r, however, this range (unnecessarily) extends
up to 800 in the S3 section for example. Most likely, 200 would be
largely enough, does it imply a sizable reduction on the iterative
reconstruction noise levels ? Besides, iterative delensing is
complicated and not established yet, in contrast to Quadratic
Estimator delensing. The paper might gain in interest if numbers for
Q.E. and iterative delensing were presented.

\vspace{0.4cm}

%One information that is probably not clear enough or partially missing in the text is that iterative delensing compared to iterative delensing is important only for CMB-S4 noise levels. 
%For example, the amount of BB power removed for CMB-S3 level using iterative vs. QE is 51\% vs. 56\%.

Let me start from the first part of the comment which regards the scales used here.
The idea of a separation in scale between the CMB data used to reconstruct the potential and the data used to constrained r, is indeed an interesting idea proposed (for example in \cite{sehgal:2017}) to solve the so-called "internal delensing bias". This is important for both QE and iterative approach. This and other methods have shown that, at least on simulations, we can avoid this bias \textit{without losing performance}. 
Other groups have shown that it is possible to use overlapping scales and then correct for the bias.
For this reason, we can reconstruct the lensing potential using scales that overlap with the primordial B-mode, without being over-optimistic. 
While a full treatment of this effects with realistic simulations is important, we left a full study for future works.
Again this can also be tested on data. For example, the deep 100 deg$^{2}$ field measured by SPTPol that can reach a depth of $5-6 ~\mu$K arcmin with high resolution might be the first dataset where this can be explored.

Regarding the second part of the comment, I agree that it is interesting to quickly investigate the loss in performance if the quadratic estimator is used instead of the iterative one. For this reason, I added a new case for S3 and S4 experiment: the quadratic estimator case. Since this is a widely used technique, I think it can be presented without much introduction. I added a few sentences at the end of section IIA and in the S3 and S4 sections. Note that there is no difference between these two approaches for current levels of noise (S2).

### 2017-12-04 Notes/galaxy_delensing.tex
working on referee response

\begin{table}
\caption{$\alpha$: Improvements on $\sigma(r)$ due to delensing for S3 experiments. Here we define LSS-S3 as the combination of S2 LSS tracers (LSS-S2) and DESI. We also use a CMB S3 experiment for the lensing internal reconstruction. The error $\sigma(r)$ is computed using \refeq{fisher} with $50<\ell<800$, see \refsec{S3} for details.}
%The absolute error value of $\sigma(r)$ after delensing for $f_{sky} = $ is $\sigma(r) =$ 
\hspace{2.2cm}
\begin{tabular}{|c | c | c | c|}
\hline
Surveys & $\alpha_{r=0}, N^{B}_{\ell}=0$ & $\alpha_{r=0}$ & $\alpha_{r=0.07}$ \\ \hline \hline
DESI (11\%) &1.13 & 1.1  & 1.04 \\ \hline
LSS-S3 (45\%) &1.82& 1.59  & 1.18\\ \hline
CMB 3G (56\%) &2.31& 1.9  & 1.23 \\ \hline
LSS-S3+CMB (68\%)& 3.17 & 2.3& 1.30  \\ \hline
\end{tabular}
\label{tab:S3}
\end{table}

@@

\begin{table}
\caption{$\alpha$: Improvements on $\sigma(r)$ and $\sigma(n_{t})$ after delensing for S4 experiments. Here we define LSS-S4 as the combination of S3 LSS tracers (LSS-S3) and LSST. We also consider SKA-like radio-continuum surveys. We also use a CMB S4 experiment for the lensing internal reconstruction. The improvement for $\sigma(n_{t})$ is computed for fiducial values $r=0.07$ and $n_t=-r/8$. The error $\sigma(r)$ is computed using \refeq{fisher} with $50<\ell<800$ see \refsec{S4} for details.}
\begin{tabular}{|c | c | c | c| c|}
\hline
Surveys & $\alpha_{r=0}, N^{B}_{\ell}=0$ & $\alpha_{r=0}$ & $\alpha_{r=0.07}$ & $\alpha^{n_{t}}_{r=0.07}$ \\ \hline \hline
LSST (51\%) &2.1 & 1.9  & 1.21 & 1.47 \\ \hline
LSS-S4  (59\%) &2.4 & 2.1  & 1.25 & 1.57\\ \hline
SKA (10$\mu$Jy) (53\%) &2.1& 1.9  & 1.22& 1.46\\ \hline
LSS-S4 + SKA (62\%) &2.6 & 2.3  & 1.3& 1.6  \\ \hline
CMB S4 (83\%) & 6.22 & 4.1  & 1.42& 2.3 \\ \hline
LSS-S4+CMB (86\%)& 7.7 & 4.7  & 1.46 & 2.46\\ \hline
\end{tabular}
\label{tab:S4}
\end{table}

>>>>

\begin{table}
\caption{$\alpha$: Improvements on $\sigma(r)$ due to delensing for S3 experiments. Here we define LSS-S3 as the combination of S2 LSS tracers (LSS-S2) and DESI. We also use a CMB S3 experiment for the lensing internal reconstruction. The error $\sigma(r)$ is computed using \refeq{fisher} with $50<\ell<800$, see \refsec{S3} for details.}
%The absolute error value of $\sigma(r)$ after delensing for $f_{sky} = $ is $\sigma(r) =$ 
\hspace{2.2cm}
\begin{tabular}{|c | c | c | c|}
\hline
Surveys & $\alpha_{r=0}, N^{B}_{\ell}=0$ & $\alpha_{r=0}$ & $\alpha_{r=0.07}$ \\ \hline \hline
DESI (11\%) &1.13 & 1.1  & 1.04 \\ \hline
LSS-S3 (45\%) &1.82& 1.59  & 1.18\\

\hline
CMB 3G (QE) (51\%) &2.0& 1.68  & 1.20 \\ 
\hline
CMB 3G (56\%) &2.31& 1.9  & 1.23 \\ \hline
LSS-S3+CMB (68\%)& 3.17 & 2.3& 1.30  \\ \hline
\end{tabular}
\label{tab:S3}
\end{table}

@@

\begin{table}
\caption{$\alpha$: Improvements on $\sigma(r)$ and $\sigma(n_{t})$ after delensing for S4 experiments. Here we define LSS-S4 as the combination of S3 LSS tracers (LSS-S3) and LSST. We also consider SKA-like radio-continuum surveys. We also use a CMB S4 experiment for the lensing internal reconstruction. The improvement for $\sigma(n_{t})$ is computed for fiducial values $r=0.07$ and $n_t=-r/8$. The error $\sigma(r)$ is computed using \refeq{fisher} with $50<\ell<800$ see \refsec{S4} for details.}
\begin{tabular}{|c | c | c | c| c|}
\hline
Surveys & $\alpha_{r=0}, N^{B}_{\ell}=0$ & $\alpha_{r=0}$ & $\alpha_{r=0.07}$ & $\alpha^{n_{t}}_{r=0.07}$ \\ \hline \hline
LSST (51\%) &2.1 & 1.9  & 1.21 & 1.47 \\ \hline
LSS-S4  (59\%) &2.4 & 2.1  & 1.25 & 1.57\\ \hline
SKA (10$\mu$Jy) (53\%) &2.1& 1.9  & 1.22& 1.46\\ \hline
LSS-S4 + SKA (62\%) &2.6 & 2.3  & 1.3& 1.6  \\ \hline
CMB S4 (QE) (73\%) & 3.7 & 2.9  & 1.35& 2.3 \\ \hline
CMB S4 (83\%) & 6.22 & 4.1  & 1.42& 2.3 \\ \hline
LSS-S4+CMB (86\%)& 7.7 & 4.7  & 1.46 & 2.46\\ \hline
\end{tabular}
\label{tab:S4}
\end{table}
